---
title: "Accuracy_CI"
author: "Oliver Dürr"
date: "3/27/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Accuracy CI (not weighted)

### Creation of some random data

```{r}
  create_preds = function(y_true) {
    weights = nclasses/n
    y_pred = y_true
    for (i in 1:length(y_pred)) {
      # Get a random index in 20 precent
      if (sample(c(TRUE, FALSE),1, prob = c(0.2,0.8))) {
        y_pred[i] = sample(c(1,2,3), size = 1, prob=weights)
      }
    } 
    return (y_pred)
  }

  nclasses = c(10,100,200) #Number of classes in the training set 
  n = sum(nclasses)
  y_true = c(rep(1, nclasses[1]), rep(2, nclasses[2]), rep(3, nclasses[3])) #True_labels in the testset
  y_pred = create_preds(y_true)
  acc = mean(y_pred == y_true) 
```
The single sample of random dataset has an accuracy of `r acc`.

### Getting the true distribution of the accuracy
```{r}
 accs = rep(NA, 1500)
 for (r in 1:length(accs)) {
   y_pred = create_preds(y_true)
   accs[r] = mean(y_pred == y_true) 
 }
 hist(accs, sqrt(length(accs)))
```
```{r}
  q2 = quantile(accs, 0.975) 
  q1 = quantile(accs, 0.025)
  novel_sample= c(q1,q2)
  ci_sample = q2 - q1
```

The sampled 95% CI should be approx from `r q1` to `r q2` and the range `r ci_sample`.

### Calculating the CI for the accuracy (Willson Method) 

First, we use the Wilson score intervall, see e.g. https://machinelearningmastery.com/report-classifier-performance-confidence-intervals/

```{r}
  acc_ci = acc + c(qnorm(0.025), qnorm(0.975)) * sqrt( (acc * (1 - acc)) / n)
  cat(acc_ci, acc_ci[2]-acc_ci[1])
```
### Calculating the CI using bootstrap
```{r}
  library(boot)
  df = data.frame(y_true, y_pred)
  acc.func = function(data, ind) {
    mean(y_true[ind] == y_pred[ind])
  }
  r.boot <- boot(df, R = 1000, statistic = acc.func)
  r.boot
```
#### Calculation of the CI 

We now calculate the CI from the bootstrap samples using different techniques:

* Assuming a normal distribution (like in the Wilson CI)
* Using the quantiles
* Using a method called BCA (I forget what that was)

```{r}
  se = sd(r.boot$t)
  ci_norm = r.boot$t0 + c(qnorm(0.025), qnorm(0.975)) * se
  d = boot.ci(boot.out = r.boot, conf = 0.95, type = "bca")
  ci_quant = quantile(r.boot$t, c(0.025, 0.975))
  ci_bca = c(d$bca[4],d$bca[5]) 
  res_df = data.frame(ci_norm, ci_quant, ci_bca, wilson_ci = acc_ci, novel_sample)
  res_df = rbind(res_df, res_df[2,] - res_df[1,])
  rownames(res_df)[3] = 'range of CI'
  res_df
```

Looks like that the bootstrap CI shows a lower accuracy than the Willson and Novel Sample



## Accuracy CI (Weighted)
Now we calculate the weighted accuracy. We do this by calculating the accuracys for the individal classes.

```{r}
  # We use ind to compatible with the bootstrap version
  acc.func = function(data, ind) {
    #ind = 1:310
    y_t = data$y_true[ind]
    y_p = data$y_pred[ind]
    acc = 0
    for (clazz in 1:3) {
      idx = y_t == clazz
      acc = acc + mean(y_t[idx] == y_p[idx])
    }
    return (acc / 3)
  }
  acc.func(df, 1:n)
```

#### Sampling on new data
```{r}
   accs_w = rep(NA, 1000)
   for (r in 1:length(accs_w)) {
     y_pred = create_preds(y_true)
     accs_w[r] = acc.func(data.frame(y_true, y_pred), 1:310)
   }
   hist(accs_w, sqrt(length(accs_w)))
```

And calulating the accuracy 
```{r}
  q2_w = quantile(accs_w, 0.975) 
  q1_w = quantile(accs_w, 0.025)
  novel_sample_w= c(q1_w,q2_w)
  ci_sample = q2_w - q1_w
```
The sampled 95% CI should be approx from `r q1` to `r q2` and the range `r ci_sample`.


#### Bootstrapping
```{r}
  library(boot)
  r.boot <- boot(data.frame(y_true, y_pred), R = 1000, statistic = acc.func)
  r.boot
```
```{r}
  se = sd(r.boot$t)
  ci_norm = r.boot$t0 + c(qnorm(0.025), qnorm(0.975)) * se
  d = boot.ci(boot.out = r.boot, conf = 0.95, type = "bca")
  ci_quant = quantile(r.boot$t, c(0.025, 0.975))
  ci_bca = c(d$bca[4],d$bca[5]) 
  res_df_w = data.frame(ci_norm, ci_quant, ci_bca,novel_sample_w)
  res_df_w = rbind(res_df_w, res_df_w[2,] - res_df_w[1,])
  rownames(res_df_w)[3] = 'range of CI'
  res_df_w
```



